---
title: "PLSPM-Values"
geometry: margin=0.2cm
output:
  pdf_document: default
  html_document: default
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=8, fig.height=10)

```

```{r, results='hide', warning=FALSE, echo=FALSE, message=FALSE}
source("LoadData.R", encoding = "UTF-8")
source("Stats_functions.R")
source("PLS_functions.R")
```
# Analyse PLSPM - Influence des traits de personnalité sur le flow et l'engagement

## ----------- TESTS AVEC INNER MODEL "PARFAIT" (vérif outer model only) -----------
### Outer Model Check for Traits
```{r, warning=FALSE, echo=FALSE, message=FALSE}
aest_pls = pls_traits(aesthetic_df)
narr_pls = pls_traits(narrative_df)
goal_pls = pls_traits(objectives_df)

knit_plspm_results(aest_pls, "Aesthetic")
```

### Outer Model Check for Flow and Engagement
```{r, warning=FALSE, echo=FALSE, message=FALSE}
all_pls = pls_dfs_eng(traits_dfs_df = traits_dfs_df)

aest_pls = pls_dfs_eng(aesthetic_df)
narr_pls = pls_dfs_eng(narrative_df)
goal_pls = pls_dfs_eng(objectives_df)

knit_plspm_results(all_pls, "All Scenario")

# knit_plspm_results(aest_pls, "Aesthetic")
# 
# knit_plspm_results(narr_pls, "Narrative")
# 
# knit_plspm_results(goal_pls, "Goals")
```

### Outer Model Check for Traits, Flow and Engagement
```{r echo=FALSE, message=FALSE, warning=FALSE}
#all_pls = pls_traits_dfs_eng(traits_dfs_df = traits_dfs_df)

latex_surcharged = knit_plspm_results(all_pls, "All Scenario", latex = TRUE)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
all_pls_adjusted = pls_traits_dfs_eng_adjusted_1(traits_dfs_df = traits_dfs_df)

latex_surcharged = knit_plspm_results(all_pls_adjusted, "All Scenario", latex = TRUE)

fileConn<-file("latex_surcharged.txt")
writeLines(latex_surcharged[[1]], fileConn)
close(fileConn)
```

## ----------- Modele initial / Tous les constructs / Tous les items -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=7, color_lim = NULL)

knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```
## ----------- Adjusted Models
### ----------- Constructs deleted : Aesthetic & Engagement / All Items -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=8, color_lim = NULL)


knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```
### ----------- Construct deleted : Engagement / REMOVE AEST3, AEST4, NARR5 -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=9, color_lim = NULL)


knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```
### ----------- REMOVE AEST3, AEST4, ENG1, ENG5 -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=10, color_lim = NULL, bootstrap = TRUE, bsr = 5000)


knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")

save_plspm(tab[[1]][["path_coefs"]], tab[[1]][["p_values"]], "Aesthetic")
save_plspm(tab[[2]][["path_coefs"]], tab[[2]][["p_values"]], "Narrative")
save_plspm(tab[[3]][["path_coefs"]], tab[[3]][["p_values"]], "Goals")

```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=7, color_lim = NULL)

knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```