---
title: "PLSPM-Means"
geometry: margin=0.2cm
output:
  pdf_document: default
  html_document: default
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=8, fig.height=10)

```

```{r, results='hide', warning=FALSE, echo=FALSE, message=FALSE}
source("LoadData.R", encoding = "UTF-8")
source("Stats_functions.R")
source("PLS_functions.R")
```
# Analyse PLSPM - Influence des traits de personnalité sur le flow et l'engagement

## ----------- Initial Model
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=13, color_lim = NULL)

knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```
## ----------- Adjusted Models
### ----------- Constructs deleted : Aesthetic & Engagement / All Items -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=14, color_lim = NULL)


knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```
### ----------- Construct deleted : Engagement / -AEST4 -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=15, color_lim = NULL)


knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```
### ----------- Construct deleted : Engagement / -AEST3 & AEST4 -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=16, color_lim = NULL)


knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```
### ----------- Construct deleted : Engagement / REMOVE AEST3 & AEST4, CHAL2, GOAL2, NARR5, SOCI5 -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=17, color_lim = NULL)


knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```
### ----------- Construct deleted : Engagement & Aesthetic / REMOVE CHAL2, GOAL2, NARR5, SOCI5 -----------
```{r, warning=FALSE, echo=FALSE, message=FALSE}
tab = pls_analysis(aesthetic_df, narrative_df, objectives_df,
             "Aesthetic Scenario", "Narrative Scenario", "Goals Scenario",
             type=18, color_lim = NULL)


knit_plspm_results(tab[[1]][["traits_dfs_pls"]], "Aesthetic")

knit_plspm_results(tab[[2]][["traits_dfs_pls"]], "Narrative")

knit_plspm_results(tab[[3]][["traits_dfs_pls"]], "Goals")
```