---
title: "SEM_ANALYSIS"
geometry: margin=0.2cm
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# SEM Analysis : Influence of player Traits on Flow in Virtual Reality
## SEM for Traits using Lavaan

```{r, results='hide', warning=FALSE, echo=FALSE, message=FALSE}
library(lavaan)
source("LoadData.R", encoding = "UTF-8")
source("Stats_functions.R")
source("PLS_functions.R")
source("SEM_functions.R")
```


```{r}
traits_data = sem_traits_data(aesthetic_df)
```
### Traits Model
```{r}
traits_model <- '
# measurement model
Aesthetic =~ AEST1 + AEST2 + AEST3 + AEST4 + AEST5
Challenge =~ CHAL1 + CHAL2 + CHAL3 + CHAL4 + CHAL5
Goals =~ GOAL1 + GOAL2 + GOAL3 + GOAL4 + GOAL5
Narrative =~ NARR1 + NARR2 + NARR3 + NARR4 + NARR5
Social =~ SOCI1 + SOCI2 + SOCI3 + SOCI4 + SOCI5
'

fit_traits_model <- sem(traits_model, data=traits_data)

summary(fit_traits_model, standardized=TRUE, fit.measures=TRUE)
```
### Adjusted Traits Models
#### Adjusted on Aesthetic 
Adjustment : Remove AEST4
```{r}
traits_model <- '
# measurement model
Aesthetic =~ AEST1 + AEST2 + AEST3 + AEST5
Challenge =~ CHAL1 + CHAL2 + CHAL3 + CHAL4 + CHAL5
Goals =~ GOAL1 + GOAL2 + GOAL3 + GOAL4 + GOAL5
Narrative =~ NARR1 + NARR2 + NARR3 + NARR4 + NARR5
Social =~ SOCI1 + SOCI2 + SOCI3 + SOCI4 + SOCI5
'

fit_traits_model <- sem(traits_model, data=traits_data)

summary(fit_traits_model, standardized=TRUE, fit.measures=TRUE)
```

#### Adjusted on All Traits 
Adjustment : Remove AEST4, CHAL2, GOAL2, NARR5, SOCI5
```{r}
traits_model <- '
# measurement model
Aesthetic =~ AEST1 + AEST2 + AEST3 + AEST5
Challenge =~ CHAL1 + CHAL3 + CHAL4 + CHAL5
Goals =~ GOAL1 + GOAL3 + GOAL4 + GOAL5
Narrative =~ NARR1 + NARR2 + NARR3 + NARR4
Social =~ SOCI1 + SOCI2 + SOCI3 + SOCI4
'

fit_traits_model <- sem(traits_model, data=traits_data)

summary(fit_traits_model, standardized=TRUE, fit.measures=TRUE)
```

## SEM for Flow using Lavaan

```{r}
all_flow_data  = sem_flow_data(traits_dfs_df)
aest_flow_data = sem_flow_data(aesthetic_df)
goal_flow_data = sem_flow_data(objectives_df)
narr_flow_data = sem_flow_data(narrative_df)
```

```{r}
flow_model <- '
# measurement model
Chal.Skill.Balance =~ CSB1 + CSB2 + CSB3 + CSB4
Action.Awareness =~ AA1 + AA2 + AA3 + AA4
Clear.Goals =~ CG1 + CG2 + CG3 + CG4
Unambiguous.Fdbck =~ UF1 + UF2 + UF3 + UF4
Concentration =~ CNT1 + CNT2 + CNT3 + CNT4
Sense.of.Control =~ SOC1 + SOC2 + SOC3 + SOC4
Loss.Self.Cnscsnss =~ LSC1 + LSC2 + LSC3 + LSC4
Time.Trnsfrmtn =~ TT1 + TT2 + TT3 + TT4
Autotelic.Exprnc =~ AE1 + AE2 + AE3 + AE4
'
```
### Flow Model for All Scenario
```{r}
all_fit_flow_model <- sem(flow_model, data=all_flow_data)

summary(all_fit_flow_model, standardized=TRUE, fit.measures=TRUE)
```

## SEM for Engagement using Lavaan

```{r}
all_engagement_data  = sem_engagement_data(traits_dfs_df)
aest_engagement_data = sem_engagement_data(aesthetic_df)
goal_engagement_data = sem_engagement_data(objectives_df)
narr_engagement_data = sem_engagement_data(narrative_df)
```

```{r}
engagement_model <- '
# measurement model
Engagement =~ ENG1 + ENG2 + ENG3 + ENG4 + ENG5 + ENG6
'
```
### Default Engagement Models
#### All Scenario

```{r}
all_fit_engagement_model <- sem(engagement_model, data=all_engagement_data)

summary(all_fit_engagement_model, standardized=TRUE, fit.measures=TRUE)
```

#### Aesthetic Scenario

```{r}
aest_fit_engagement_model <- sem(engagement_model, data=aest_engagement_data)

summary(aest_fit_engagement_model, standardized=TRUE, fit.measures=TRUE)
```

#### Narrative Scenario

```{r}
narr_fit_engagement_model <- sem(engagement_model, data=narr_engagement_data)

summary(narr_fit_engagement_model, standardized=TRUE, fit.measures=TRUE)
```

#### Goals Scenario

```{r}
goal_fit_engagement_model <- sem(engagement_model, data=goal_engagement_data)

summary(goal_fit_engagement_model, standardized=TRUE, fit.measures=TRUE)
```

### Adjusted Engagement Models
#### All Scenario 
Adjustment : Remove ENG5 and ENG6

```{r}
engagement_model <- '
# measurement model
Engagement =~ ENG1 + ENG2 + ENG3 + ENG4
'
```

```{r}
all_fit_engagement_model <- sem(engagement_model, data=all_engagement_data)

summary(all_fit_engagement_model, standardized=TRUE, fit.measures=TRUE)
```

#### Aesthetic Scenario

```{r}
aest_fit_engagement_model <- sem(engagement_model, data=aest_engagement_data)

summary(aest_fit_engagement_model, standardized=TRUE, fit.measures=TRUE)
```

#### Narrative Scenario

```{r}
narr_fit_engagement_model <- sem(engagement_model, data=narr_engagement_data)

summary(narr_fit_engagement_model, standardized=TRUE, fit.measures=TRUE)
```

#### Goals Scenario

```{r}
goal_fit_engagement_model <- sem(engagement_model, data=goal_engagement_data)

summary(goal_fit_engagement_model, standardized=TRUE, fit.measures=TRUE)
```


<!-- ### Flow Model for Aesthetic Scenario -->
<!-- ```{r} -->
<!-- aest_fit_flow_model <- sem(flow_model, data=aest_flow_data) -->

<!-- summary(aest_fit_flow_model, standardized=TRUE, fit.measures=TRUE) -->
<!-- ``` -->

<!-- ### Flow Model for Goals Scenario -->
<!-- ```{r} -->
<!-- goal_fit_flow_model <- sem(flow_model, data=goal_flow_data) -->

<!-- summary(goal_fit_flow_model, standardized=TRUE, fit.measures=TRUE) -->
<!-- ``` -->

<!-- ### Flow Model for Narrative Scenario -->
<!-- ```{r} -->
<!-- narr_fit_flow_model <- sem(flow_model, data=narr_flow_data) -->

<!-- summary(narr_fit_flow_model, standardized=TRUE, fit.measures=TRUE) -->
<!-- ``` -->

<!-- ## PLS-SEM Model -->
<!-- ```{r} -->
<!-- traits_flow_model <- ' -->
<!-- # Traits Measurement Model -->
<!-- Aesthetic =~ AEST1 + AEST2 + AEST3 + AEST5 -->
<!-- Challenge =~ CHAL1 + CHAL3 + CHAL4 + CHAL5 -->
<!-- Goals =~ GOAL1 + GOAL3 + GOAL4 + GOAL5 -->
<!-- Narrative =~ NARR1 + NARR2 + NARR3 + NARR4 -->
<!-- Social =~ SOCI1 + SOCI2 + SOCI3 + SOCI4 -->

<!-- # Flow Measurement Model -->
<!-- Chal.Skill.Balance =~ CSB1 + CSB2 + CSB3 + CSB4 -->
<!-- Action.Awareness =~ AA1 + AA2 + AA3 + AA4 -->
<!-- Clear.Goals =~ CG1 + CG2 + CG3 + CG4 -->
<!-- Unambiguous.Feedback =~ UF1 + UF2 + UF3 + UF4 -->
<!-- Concentration =~ CNT1 + CNT2 + CNT3 + CNT4 -->
<!-- Sense.of.Control =~ SOC1 + SOC2 + SOC3 + SOC4 -->
<!-- Loss.Self.Consciousness =~ LSC1 + LSC2 + LSC3 + LSC4 -->
<!-- Time.Transformation =~ TT1 + TT2 + TT3 + TT4 -->
<!-- Autotelic.Experience =~ AE1 + AE2 + AE3 + AE4 -->

<!-- # Regression -->
<!-- Chal.Skill.Balance ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- Action.Awareness ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- Clear.Goals ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- Unambiguous.Feedback ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- Concentration ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- Sense.of.Control ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- Loss.Self.Consciousness ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- Time.Transformation ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- Autotelic.Experience ~ Aesthetic + Challenge + Goals + Narrative + Social -->
<!-- ' -->
<!-- ``` -->

<!-- ```{r} -->
<!-- all_traits_flow_data = rbind(cbind(traits_data, aest_flow_data), cbind(traits_data, goal_flow_data), cbind(traits_data, narr_flow_data)) -->

<!-- all_fit_traits_flow_model <- sem(traits_flow_model, data=all_traits_flow_data) -->

<!-- summary(all_fit_traits_flow_model, standardized=TRUE, fit.measures=TRUE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- aest_traits_flow_data = cbind(traits_data, aest_flow_data) -->

<!-- aest_fit_traits_flow_model <- sem(traits_flow_model, data=aest_traits_flow_data) -->

<!-- summary(aest_fit_traits_flow_model, standardized=TRUE, fit.measures=TRUE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- goal_traits_flow_data = cbind(traits_data, goal_flow_data) -->

<!-- goal_fit_traits_flow_model <- sem(traits_flow_model, data=goal_traits_flow_data) -->

<!-- summary(goal_fit_traits_flow_model, standardized=TRUE, fit.measures=TRUE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- narr_traits_flow_data = cbind(traits_data, narr_flow_data) -->

<!-- narr_fit_traits_flow_model <- sem(traits_flow_model, data=narr_traits_flow_data) -->

<!-- summary(narr_fit_traits_flow_model, standardized=TRUE, fit.measures=TRUE) -->
<!-- ``` -->